Stage-Splitting a Modal Language

### 2014-05-27 paper/sigplanconf-template.tex
first draft of reference semantics in
Added raw code for two examples.

\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{bbm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{mathabx}

@@

\begin{center}
\begin{tabular}{l}
If $\splittwo{e}{A}{p,l.r}$ \\
and $\reducetwo{e}{v}$ \\
then $\reduce{p}{u}$ \\
and $\reduce{[u/l]r}{w}$ \\
and $v = w$ 
\end{tabular}
\end{center}

@@

Fast exponent example.  Quickselect example.

>>>>

\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{bbm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{mathabx}
\usepackage{listings}

@@

%\begin{center}
%\begin{tabular}{l}
%If $\splittwo{e}{A}{p,l.r}$ \\
%and $\reducetwo{e}{v}$ \\
%then $\reduce{p}{u}$ \\
%and $\reduce{[u/l]r}{w}$ \\
%and $v = w$ 
%\end{tabular}
%\end{center}

@@

Fast exponent example.

\lstset{language=ML, basicstyle=\ttfamily, tabsize=4, escapeinside={"*}{*"}}
\begin{lstlisting} 
let exp (b : $int, e : int) : $int =
	if e == 0 then
		next{1}
	else if (e mod 2) == 0 then
		next{let x = prev{exp(b,e/2)} in x*x}
	else
		next{prev{b} * prev{exp (b,e-1)}}		
\end{lstlisting}

splits into

\begin{lstlisting} 
let exp (b, e) =
	((), roll (
		if e == 0 then
			inL ()
		else 
			inR (
				if (e mod 2) == 0 then
					inL (#2 (exp (b,e/2)))
				else
					inR (#2 (exp (b,e-1)))
			)
	))
\end{lstlisting}

and

\begin{lstlisting} 
let exp ((b, e), p) =
	case unroll p of
	  () => 1
	| d  =>
		case d of
		  r => let x = exp ((b,()),r) in x*x
		| r => b * exp ((b,()),r)
\end{lstlisting}

Quickselect example.

\begin{lstlisting} 
let qs (l : "*$\mathtt{\mu \alpha. }$*"() + "*$\mathtt{int*\alpha}$*", i: $int) = 
	case unroll l of
	  () => next {0}
	| (h,t) => 
		let (left,right,n) = partition h t in
		next{
			let n = prev{hold n} in
			case compare prev{i} n of
			  () (*LT*) => prev {qs left i}
			| () (*EQ*) => hold h
			| () (*GT*) => 
				prev {qs right next{prev{i}-n-1}}
		}	
\end{lstlisting}
